Collocated Deduplication with Fault Isolation for Virtual Machine Snapshot Backup

### 2013-08-28 snapshot_system/concl.tex
update eval
revise eval1.tex

\section{Conclusion}
\label{sect:final}
In this paper we propose a VM-centric deduplication scheme for 
VM snapshot backup in the cloud for maximizing fault isolation and tolerance. 
Inner-VM deduplication localizes backup data dependency and exposes more parallelism  
while cross-VM deduplication with a small common data set
effectively  covers a large percent of duplicate data.
The scheme organizes the write of small data chunks into large file system blocks so
that each underlying file block is associated with one VM for most cases.
by keeping most of the FSBs only referenced by 1 VM, we isolate faults and improve overal fault tolerance.
Our solution accomplishes reasonable and competitive deduplication efficiency while
still meeting stringent cloud resource usage requirements. 
Our analysis shows that  this VM centric scheme 
can  provide  better fault tolerance than VM-oblivious global deduplication schemes
while using a small amount of computing and storage resources.

[Talk about more what we learn from Evaluation]
Evaluation using real user's VM data shows
our solution can accomplish 92\% of what complete global
deduplication can do. 
Compare to today's widely-used snapshot technique, our scheme reduces almost
two-third of snapshot storage cost.
Finally, our scheme uses a very small amount of memory on each node, and leaves
room for additional optimization we are further studying.

>>>>

\section{Conclusion}
\label{sect:final}
In this paper we propose a collocated backup service built on
the top of a cloud cluster to reduce network traffic and infrastructure.
The key contribution is a VM-centric deduplication scheme to 
maximize fault isolation while delivering competitive deduplication efficiency.
Inner-VM deduplication localizes backup data dependency and exposes more parallelism  
while cross-VM deduplication with a small common data set.
VM-specific file block packing also reduces inter-VM dependence and enhances fault tolerance.
The design places a special consideration for low-resource usages as a collocated cloud service.
Evaluation using  VM backup data shows that
our solution can accomplish 92\% of what complete global
deduplication can do while the availability of snapshots increases substantially with this VM-centric
and a small replication overhead for popular inter-VM chunks.

% effectively  covers a large percent of duplicate data.
%The scheme organizes the write of small data chunks into large file system blocks so
%that each underlying file block is associated with one VM for most cases.
%by keeping most of the FSBs only referenced by 1 VM, we isolate faults and improve overal fault tolerance.
%Our solution accomplishes reasonable and competitive deduplication efficiency while
%still meeting stringent cloud resource usage requirements. 
%Our analysis shows that  this VM centric scheme 
%can  provide  better fault tolerance than VM-oblivious global deduplication schemes
%while using a small amount of computing and storage resources.

%[Talk about more what we learn from Evaluation]
%Compare to today's widely-used snapshot technique, our scheme reduces almost
%two-third of snapshot storage cost.
%Finally, our scheme uses a very small amount of memory on each node, and leaves
%room for additional optimization we are further studying.
